---
title: "A Neighborhood Question"
subtitle: "Staff Meeting, January 2016"
author: "Tiernan Martin | [tiernan@futurewise.org](tiernan@futurewise.org)"
date: "January 11, 2016"
output:
  ioslides_presentation:
    widescreen: true
        
---

```{r setup, include=FALSE}
options(scipen =999,stringsAsFactors = FALSE)

knitr::opts_chunk$set(echo = FALSE,warning=FALSE,message=FALSE,tidy = TRUE)
library(htmlwidgets)
library(readr)
library(dplyr)
library(knitr)
library(magrittr)
library(rgdal)
library(leaflet)
library(RColorBrewer)
library(gplots)
library(rgeos)



```

## The Purposes of this Presentation {.build}
> 1. **Practice**
>     + dry run so I can work through some kinks
>     + on the my question and how it is presented
>          + on the my question and how it is presented
>
> 2. **Get feedback **
>     + on the my question and how it is presented
>     + on the approach you think would be best and why
>
> 3. **Introduce my skill set**
>     + GIS
>     + R Statsical Programming Language

## Project overview
We're creating a baseline conditions report for the Yesler Community Collaborative. The report will be provide the project's partners with a data-rich snapshot of Yesler Terrace and the neighborhoods that surround it.

###Primary Goal
- Convey how the neighborhoods compare to each other (as well as to Seattle as a whole) across the typical range of topics

### Secondary Goal
- Provide the project partners with data that they can use to create their own graphs and visuals (i.e, cleaned, processed, and aggregated data sets)


## Introduction to R 

```{r}

medInc <- read_csv(file = "medianIncome2014.csv") 
DT::datatable(medInc)

```

## An Interactive Map: Median Household Income

<iframe  title="Median Household Income" width="980" height="400" src="http://tiernanmartin.github.io/FW-YCC-Baseline-Conditions/4_webcontent/lflt_medHhInc.html" frameborder="0" allowfullscreen></iframe>
